Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-13 paper/disc20clustering.tex
small

\mahmoud{
	If a feasible partition exists 
	that collocates the new ground set $\{x_i,\} \cup C $,  
	then $x_i$ is replaced by some isolated node
	 $x_{i+1} \not\in \{y_0, x_0, \dots, x_i\}$.
%	 similarly to $x_0$, and we continue creating such ground sets.
%	We describe the termination condition shortly.
	Otherwise,
	the current partition is not feasible,
	 we terminate the process and we let $x^* := x_i, y^*:=y_i$. 
	 At this point,
	 there are at most $\ell$ isolated nodes left.
	 Assume for contradiction that this is not the case,
	 i.e., there are at least $\ell+1$ isolated nodes left.
	 Then there must be two isolated nodes $u$ and $v$ with the same cluster of origin,
	 i.e., $I(\{u\}) = I(\{v\})$.
	 Consider the partition $P$,
	  obtained from the initial partition after swapping $x_0$ and $y_0$
	 with $u$ and $v$ (respectively).
	 In this partition,
	 the ground set $\{x_0,y_0\}$ is collocated in the cluster $I(\{u,v\})$.
	 Note that after the first request $\{x_0,y_0\}$,
	   we issue requests only between nodes that have the same cluster of origin and
	   all these nodes are collocated in $P$.
	 Therefore $P$  has all ground sets constructed so far collocated, i.e.,
	 it is a feasible partition, which contradicts our assumption.
}

>>>>

\mahmoud{
	If a feasible partition exists 
	that collocates the new ground set $\{x_i,\} \cup C $,  
	then $x_i$ is replaced by some isolated node $x_{i+1}$.
%	 similarly to $x_0$, and we continue creating such ground sets.
%	We describe the termination condition shortly.
	Otherwise,
	the current partition is not feasible,
	 we terminate the process and we let $x^* := x_i, y^*:=y_i$. 
	 At this point,
	 there are at most $\ell$ isolated nodes left.
	 Assume for contradiction that this is not the case,
	 i.e., there are at least $\ell+1$ isolated nodes left.
	 Then there must be two isolated nodes $u$ and $v$ with the same cluster of origin,
	 i.e., $I(\{u\}) = I(\{v\})$.
	 Consider the partition $P$,
	  obtained from the initial partition after swapping $x_0$ and $y_0$
	 with $u$ and $v$ (respectively).
	 In this partition,
	 the ground set $\{x_0,y_0\}$ is collocated in the cluster $I(\{u,v\})$.
	 Note that after the first request $\{x_0,y_0\}$,
	   we issue requests only between nodes that have the same cluster of origin and
	   all these nodes are collocated in $P$.
	 Therefore $P$  has all ground sets constructed so far collocated, i.e.,
	 it is a feasible partition, which contradicts our assumption.
}
